%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\itemsep}{-2pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Jacob Hunter} \\ \vspace{1pt}
    Tucson, AZ | \vspace{1pt} TS/SCI Clearance \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 916-259-6898 ~ \href{mailto:jacobguinhunter@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{jacobguinhunter@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/jacobghunter/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/jacobghunter/}}  ~
    \href{https://github.com/jacobghunter}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/jacobghunter}}
    \vspace{-8pt}
\end{center}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Rincon Research Corporation}{Feb 2025 - Present}
      {Engineer/Scientist 1}{Tucson, AZ}
      \resumeItemListStart
      
        \item[] \hspace*{-12pt}\textbf{Racecar} / High-Throughput Data Streaming Platform
        \resumeItem{Achieved a 4x reduction in Core Web Vitals (FCP/LCP) and eliminated Layout Shift (CLS) by optimizing the Vite/Nginx build pipeline, refactoring blocking Vue.js watchers, and implementing application-wide code splitting.}
        \resumeItem{Built an AI-powered search engine web app integrated into the Racecar platform, contributing to system-wide design decisions for LLM-driven data retrieval with multi-modal visualizations including geospatial mapping and a vector image gallery with persistent chat history.}        
        \resumeItem{Owned a ground-up visual redesign of the entire Racecar web application in Quasar, overhauling every screen to deliver a modern, accessible interface with responsive layouts, tab-navigable flows, and developer keybinds, significantly reducing friction for non-technical users.}
        \resumeItem{Architected a GitLab CI/CD pipeline integrating automated Lighthouse regression testing and containerized Docker builds to enforce Core Web Vitals performance standards across deployments.}    
        
        \item[] \hspace*{-12pt}\textbf{Hercules} / AI Object Detection Pipeline
        \resumeItem{Engineered an automated incremental learning pipeline processing tens of thousands of daily images, implementing a Python workflow to ingest, normalize, and convert continuous data streams into COCO format for real-time model refinement.}
        \resumeItem{Architected a scalable Inter-Process Communication (IPC) layer using Redis to orchestrate the asynchronous data ingestion and training workflow, ensuring high availability and zero data loss during throughput spikes.}
        \resumeItem{Built a real-time command dashboard in Vue.js and ECharts visualizing live training metrics, model convergence, and lineage, backed by PostgreSQL for persistent metadata storage and performance tracking across model iterations.}
        
        \item[] \hspace*{-12pt}\textbf{SkySnare} / Drone Detection System \textit{(Internship $\rightarrow$ Full-Time)}
        \resumeItem{Co-architected and built a distributed FAA Remote ID drone tracking system, delivering a multi-node mesh network and real-time visual verification.}
        \resumeItem{Built the backend control plane in Django and a real-time React frontend deployed on AWS (EC2), utilizing WebSockets for live flight path mapping and developing a historical playback engine for flight analysis.}
        \resumeItem{Orchestrated a scalable telemetry ingestion pipeline, reliably storing continuous, real-time flight data in PostgreSQL while integrating new Software-Defined Radio (SDR) sources as hardware evolved.}
        \resumeItem{Defining data storage and web server integration requirements for an upcoming university deployment, delivering technical demonstrations to campus stakeholders to secure project agreements.} 
        \resumeItem{Delivered a company-wide \underline{"Tech Talk"} ~ \href{https://github.com/jacobghunter/SkySnare/blob/main/Final_Presentation.pdf} on the system's architecture and implementation, securing continued project funding and leadership buy-in.}
        \resumeItemListEnd    
  \resumeSubHeadingListEnd
\vspace{-16pt}


%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\underline{Chess Convolutional Neural Network}~\href{https://github.com/jacobghunter/chess-ai/tree/main/cnn}} $|$ \emph{PyTorch}}{Dec 2024}
          \resumeItemListStart
            \resumeItem{Engineered a high-performance data pipeline to process millions of chess positions, utilizing HDF5 for dynamic, out-of-core data loading to bypass VRAM limitations and accelerate training.}
            \resumeItem{Designed a custom Convolutional Neural Network (CNN) architecture integrating Residual Blocks (inspired by AlphaZero) and a specialized multi-component loss function (Piece Selection + Move Location) to optimize move prediction accuracy.}
            \resumeItem{Implemented a novel data transformation strategy, generating training labels weighted by Stockfish engine evaluations (centipawn loss) and enforcing rule compliance via a move-masking layer to zero out illegal moves during inference.}
            \resumeItem{Optimized the training dataset by standardizing perspective (White-to-move only) and utilizing bitboard representations (12x8x8), significantly reducing the dimensionality required for model convergence on resource-constrained hardware.}
          \resumeItemListEnd 
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{\underline{Custom Wireless Split Keyboard}} $|$ \emph{KiCad, FreeCAD, ZMK, Hardware}}{Present}
          \resumeItemListStart
            \resumeItem{Engineered a low-profile, ergonomic split keyboard from scratch, utilizing Ergogen for layout generation, KiCad for PCB routing, and FreeCAD for designing the 3D-printable chassis.}
            \resumeItem{Configured ZMK firmware for a complex peripheral array including dual rotary encoders and a Nice!View display, with ongoing custom driver work to integrate a TPS43 touchpad over wireless split architecture.}
            \resumeItem{Executed the end-to-end hardware manufacturing process, 3D printing components via Klipper/OrcaSlicer and hand-soldering microcontrollers, surface-mount components, and Choc V1 switches.}
          \resumeItemListEnd
          \vspace{-13pt}
    \resumeSubHeadingListEnd
\vspace{-2pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Javascript/Typescript, HTML/CSS, SCSS, SQL} \\
     \textbf{Technologies/Frameworks}{: Vue, Quasar, React, Tailwind, Nginx, Caddy, AWS, Postgres, SQLite, Firebase, Django, Docker, Grafana, GitLab CI/CD, PyTorch, Linux} \\
    }}
 \end{itemize}
 \vspace{-14pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Nevada, Reno}{Dec 2024}
      {B.S. in Computer Science [Honors], Minor in Mathematics}{Reno, NV}
  \resumeSubHeadingListEnd


\end{document}
